Language learning via recursive pragmatic reasoning

### 2013-05-31 praglearn.tex
center side captions, and clarify fig. 1 caption

@@

\begin{figure}[t]
\centering
\includegraphics[width=0.98\textwidth]{figures/emergence-composite.pdf}
% \includegraphics[width=0.48\textwidth]{figures/emergence2x2-1.pdf}
% \includegraphics[width=0.48\textwidth]{figures/emergence2x2-3.pdf} \\
% \includegraphics[width=0.48\textwidth]{figures/emergence3x3-0.pdf}
% \includegraphics[width=0.48\textwidth]{figures/emergence3x3-1.pdf} \\
\caption{\label{fig:emergence} Simulations of two pragmatic agents
  playing a naming game. Each panel shows two representative
  simulation runs, with run 1 chosen to show strong convergence and
  run 2 chosen to show relatively weaker convergence. At each stage,
  $S$ and $L$ have different, possibly contradictory posteriors over
  the conventional, consensus lexicon. From these posteriors we derive
  the probability $P(\text{$L$ understands $S$})$ (marginalizing over
  target objects and word choices), and also depict graphically $S$'s
  model of the listener, $P_{L_n}(\obj | \word, \text{$S$'s data})$,
  and $L$'s actual model, $P_{L_n}(\obj | \word, \text{$L$'s
    data})$. }
\end{figure}

>>>>

% http://www.latex-community.org/forum/viewtopic.php?f=45&t=12364
\sidecaptionvpos{figure}{c}

@@

\begin{figure}[t]
\centering
\includegraphics[width=0.98\textwidth]{figures/emergence-composite.pdf}
% \includegraphics[width=0.48\textwidth]{figures/emergence2x2-1.pdf}
% \includegraphics[width=0.48\textwidth]{figures/emergence2x2-3.pdf} \\
% \includegraphics[width=0.48\textwidth]{figures/emergence3x3-0.pdf}
% \includegraphics[width=0.48\textwidth]{figures/emergence3x3-1.pdf} \\
\caption{\label{fig:emergence} Simulations of two pragmatic agents
  playing a naming game. Each panel shows two representative
  simulation runs, with run 1 chosen to show strong convergence and
  run 2 chosen to show relatively weaker convergence. At each stage,
  $S$ and $L$ have different, possibly contradictory posteriors over
  the conventional, consensus lexicon. From these posteriors we derive
  the probability $P(\text{$L$ understands $S$})$ (marginalizing over
  target objects and word choices), and also depict graphically $S$'s
  model of the listener, $P_{L_n}(\obj | \word, \text{$S$'s data})$
  (top row within each run),
  and $L$'s actual model, $P_{L_n}(\obj | \word, \text{$L$'s
    data})$ (bottom row within each run). }
\end{figure}
